\documentclass[12pt]{letter}

% Margins for US Letter size
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}


\frenchspacing % Single space after periods
\signature{\vspace{-45pt}Maximo Machado}

\begin{document}
\begin{letter}{}
    \opening{Dear Recruiter,}
    I am currently a sophomore studying Computer Science at the Massachusetts Institute of Technology.
    I want to express my interest in the embedded software C++ intern position at Formlabs.
    Something that I value greatly in a company is a tight knight community where I feel comfortable expressing my ideas and thoughts about the projects I am a part of.
    I can definitely tell from your Tough and Soft Mudder annual events that Formlabs is exactly the type of place I would love to work at.
    With the company's emphasis on innovation and real world impact, I believe that Formlabs is a place I could excel at and I would love to join the company as an intern.

    This fall I took a class called Computation Structures that dives into the internal workings of a computer and specifically used RISC-V as the architecture to study.
    My favorite part of the class was the final project in which I designed a processor and quicksort algorithm in RISC-V assembly that was optimized for specific benchmarks.
    The interplay between writing software that takes advantage of specific design decisions of the processor I created was an incredibly satisfying experience.
    This class made me realize that I wanted to program on a level that was much more tightly entwined with the computer hardware being used and as such embedded systems seems like a great field to dive into.

    Because of this, I am starting to take strides towards becoming more experienced in the field and learning the necessary skills.
    This spring I will be taking an introduction class to embedded systems but, to get a head start, I took a class this January on C and C++.
    I have also recently acquired a Raspberry Pi so I can start working on personal projects related to the field.

    I believe that I would be a great fit for this position and I hope that we are able to talk more about the internship and my qualifications.
    The best place to contact me would be my college email, maximo@mit.edu. I hope you have a wonderful day and I look forward to speaking with you soon!
    \closing{Sincerely,}
\end{letter}
\end{document}