\documentclass[12pt]{letter}
\usepackage[hidelinks]{hyperref}

% Margins for US Letter size
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\frenchspacing
\signature{\vspace{-45pt}Maximo Machado}

\begin{document}
\begin{letter}{}
    \opening{Dear Recruiter,}
    I am currently a sophomore studying Computer Science at the Massachusetts Institute of Technology.
    I want to express my interest in the Software Engineer internship at Pure Storage.
    I deeply respect the company's mission to ensure its impact on the world is a positive one, as it is a value that can be difficult but rewarding to achieve.
    Pure Storage aligns perfectly with the values I hold and I would love to work for a company that is exploring the applications of up and coming technology
    while also contributing back to the communities it is based within.

    Just this December, I built a website, \href{https://www.spotifyplaylistmanager.net}{Spotify Playlist Manager}, that is a collection of various tools to make
    managing and manipulating Spotify playlists easier and less tedious. The idea first sparked from an issue I was having with Spotify and then expanded as I learned
    of other issues people were having and features they wanted. My first rendition of the project involved a desktop application but I realized that it was
    hard to distribute and keep compatible with multiple operating systems. As the application required an internet connection anyways, I thought it would be
    best for accessibility and ease of use if I rebuilt the application as a website. I wanted to make sure anyone could use the site, so I took measures
    like using a component library focused on accessibility and also frequently asked my friends to test out the website and give back feedback.

    Once the website was in a spot I was satisfied with, I shared it with the community and I was met with an overwhelming amount of attention.
    The site in the month of January had over 300 visitors and many people told me that they were looking for exactly these tools.
    I was elated to see that a couple weeks of my own hard work could benefit a large group of people and I certainly want to work on more projects
    that are useful not only to myself but to others and the community around me.

    For this reason, I believe that I would be a great fit for this position at Pure Storage and I hope that we are able to talk more about the internship and my qualifications.
    The best place to contact me would be my school email, maximo@mit.edu. I hope you have a wonderful day and I look forward to speaking with you soon!
    \closing{Sincerely,}
\end{letter}
\end{document}